---
title: Fclust (Fuzzy Clustering)
author: "ooki"
date: "2016/1/13"
output: html_document
---

# 0. Reference
- [CRAN fclust pdf](https://cran.r-project.org/web/packages/fclust/fclust.pdf)
- [inside-R doc](http://www.inside-r.org/packages/cran/fclust/docs/FKM.ent)

# 1. library
```{r}
library(fclust)
```

# 2. data

```{r}
## McDonald's data
data(Mc)
names(Mc)
Mc

## data normalization by dividing the nutrition facts by the Serving Size (column 1)
for (j in 2:(ncol(Mc)-1))
  Mc[,j]=Mc[,j]/Mc[,1]

## removing the column Serving Size
Mc = Mc[,-1]
```

# 3. Fuzzy Clustering

```{r}
## fuzzy k-means (excluded the factor column Type (last column))
clust <- FKM(Mc[,1:(ncol(Mc)-1)], k=6, m=1.5, stand=1)
clust
```

X : Matrix or data.frame
k : Number of clusters (default: 2)
m : Parameter of fuzziness (default: 2)
RS : Number of (random) starts (default: 1)
stand : Standardization: if stand=1, the clustering algorithm is run using standardized data (default: no standardization)
startU : Rational starting point for the membership degree matrix U (default: no rational start)
conv : Convergence criterion (default: 1e-9)
maxit : Maximum number of iterations (default: 1e+6)

U : Membership degree matrix
```{r}
clust$U
```

H : Prototype matrix
F : Array containing the covariance matrices of all the clusters (NULL for FKM)
clus : Matrix containing the indices of the clusters where the objects are assigned (column 1) and the associated membership degrees (column 2)
medoid : Vector containing the indices of the medoid objects (NULL for FKM)
value : Vector containing the loss function values for the RS starts
cput : Vector containing the computational times (user times) for the RS starts
iter : Vector containing the numbers of iterations for the RS starts
k : Number of clusters
m : Parameter of fuzziness
ent : Degree of fuzzy entropy (NULL for FKM)
b : Parameter of the polynomial fuzzifier (NULL for FKM)
vp : Volume parameter (NULL for FKM)
delta : Noise distance (NULL for FKM)
stand : Standardization (Yes if stand=1, No if stand=0)
Xca : Data used in the clustering algorithm (standardized data if stand=1)
X : Raw data
call : Matched call

