---
title: "Ex Logger"
author: "okiyuki99"
date: '`r Sys.Date()`'
output:
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    fig_width: 7
    fig_height: 4.5
    fig_caption: true
    theme: cosmo
    highlight: tango
    code_folding: show
    code_download: true
knit: (function(inputFile, encoding) { 
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_dir = "../docs/") })
---

# Summary 

* logger packageのご紹介
    * Ref : https://github.com/daroczig/logger

# libraries

```{r, message=F, warning=F}
options(scipen=10)
library(dplyr)
library(logger) # remotes::install_github('daroczig/logger')

print(packageVersion("logger"))
```

# Quick Example

```{r}
log_threshold(DEBUG)
log_info('Script starting up...')

pkgs <- available.packages()
log_info('There are {nrow(pkgs)} R packages hosted on CRAN!')

for (letter in letters) {
    lpkgs <- sum(grepl(letter, pkgs[, 'Package'], ignore.case = TRUE))
    log_level(if (lpkgs < 5000) TRACE else DEBUG,
              '{lpkgs} R packages including the {shQuote(letter)} letter')
}

log_warn('There might be many, like {1:2} or more warnings!!!')
```

# Color

Rmdじゃ色が出ない

```{r}
log_layout(layout_glue_colors)
log_threshold(TRACE)
log_info('Starting the script...')
log_debug('This is the second log line')
log_trace('Note that the 2nd line is being placed right after the 1st one.')
log_success('Doing pretty well so far!')
log_warn('But beware, as some errors might come :/')
log_error('This is a problem')
log_debug('Note that getting an error is usually bad')
log_error('This is another problem')
log_fatal('The last problem')
```

# Demo

`Rscript -e "demo(colors, package = 'logger', echo = FALSE)"`とやると出る

# Try Rscript 

````
`r ''````{r}
Rscript ex/ex_logger.R
INFO [2019-04-03 21:15:16] Starting the script...
DEBUG [2019-04-03 21:15:16] This is the second log line
TRACE [2019-04-03 21:15:16] Note that the 2nd line is being placed right after the 1st one.
SUCCESS [2019-04-03 21:15:16] Doing pretty well so far!
WARN [2019-04-03 21:15:16] But beware, as some errors might come :/
ERROR [2019-04-03 21:15:16] This is a problem
DEBUG [2019-04-03 21:15:16] Note that getting an error is usually bad
ERROR [2019-04-03 21:15:16] This is another problem
FATAL [2019-04-03 21:15:16] The last problem
`r ''````
````



