---
title: "Ex mlr iml dalex"
author: "gingi99"
date: '`r Sys.Date()`'
output:
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    fig_width: 7
    fig_height: 4.5
    fig_caption: true
    theme: cosmo
    highlight: tango
    code_folding: hide
    code_download: true
knit: (function(inputFile, encoding) { 
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_dir = "../docs/") })
---

# Summary 

* mlrを使って学習したモデルをimlとDALEXで解釈する。
* 今のところ下のGithubの写景した程度のメモ
    * Github : https://github.com/katokohaku/compareModels_with_MLR-IML/blob/master/000_setup_mlr.Rmd 
    * How to use in R model-agnostic data explanation with DALEX & iml : https://www.slideshare.net/kato_kohaku/how-to-use-in-r-modelagnostic-data-explanation-with-dalex-iml

# Preparations {.tabset .tabset-fade .tabset-pills}

## library

```{r setup, include=FALSE}
library(dplyr)
library(mlr)
library(iml)
library(DALEX)
library(knitr)
set.seed(1234)

print(packageVersion("mlr"))
print(packageVersion("iml"))
print(packageVersion("DALEX"))
```

## Data

```{r}
data(apartments, package = "DALEX")
data(apartmentsTest, package = "DALEX")

str(apartments)
```

# Task Setting

## Task

回帰のタスクを設定。taskをprintするといろいろでる

```{r}
task <- mlr::makeRegrTask(id = "ap", data = apartments, target = "m2.price")
print(task)
```

## Tune

なんやろ

```{r}
tune.ctrl <- makeTuneControlRandom()
print(tune.ctrl)
```

## Resample

```{r}
res.desc <- makeResampleDesc("CV", iters = 2)
print(res.desc)
```

# Modeling {.tabset .tabset-fade .tabset-pills}

## Model List

適用できるモデルを一覧で見ることができる

```{r listLearners}
listLearners(task) %>%
  select(class, short.name, package)
```

## setup 

```{r}
learner <- NULL
par.set <- NULL
```

## linear regression with penalty (elastincnet)

```{r setup.enet}
# getLearnerParamSet(makeLearner("regr.glmnet"))
learner[["enet"]]<- makeLearner("regr.glmnet")
par.set[["enet"]] <- makeParamSet(
  makeNumericParam("alpha", lower = 0, upper = 1),
  makeNumericParam("s",     lower = 1, upper = 10^3))
```

## random forest (RF)

```{r setup.rf}
# getLearnerParamSet(makeLearner("regr.randomForest"))
learner[["rf"]] <- makeLearner("regr.randomForest")
par.set[["rf"]] <- makeParamSet(
  makeIntegerParam("ntree", lower=50, upper=1000))
```

## Gradient Boosting Machine (GBM)

```{r setup.xgb}
# getLearnerParamSet(makeLearner("regr.gbm"))
learner[["gbm"]] <- makeLearner("regr.gbm")
par.set[["gbm"]] <- makeParamSet(
  makeIntegerParam("n.trees",           lower = 3L, upper = 50L),
  makeIntegerParam("interaction.depth", lower = 3L, upper = 20L))
```

```{r}
learner %>% print()
par.set %>% print()
```

## Paramter Tuning 

```{r tune.parset, message=FALSE}
model.labels <- names(learner)
tuned.par.set <- NULL
for(model.name in model.labels) {
  # print(model.name)
  tuned.par.set[[model.name]] <- tuneParams(
    learner[[model.name]], 
    task = task, 
    resampling = res.desc,
    par.set = par.set[[model.name]],
    control = tune.ctrl)
}
tuned.par.set %>% print()
```

## Create a new model using tuned hyperparameters

```{r setHyperPars, message=FALSE}
tuned.learner <- list()
for(model.name in model.labels) {
  
  # print(model.name)
  tuned.learner[[model.name]] <- setHyperPars(
    learner = learner[[model.name]],
    par.vals = tuned.par.set[[model.name]]$x
  )
}
tuned.learner %>% print()
```

## Re-train parameters using tuned hyperparameters (and full training set)
  
```{r tune.model, message=FALSE}
model.labels <- names(learner)
tuned.model   <- NULL
for(model.name in model.labels) {
  tuned.model[[model.name]] <- train(tuned.learner[[model.name]], task)
}
tuned.model %>% print()
```

# iml {.tabset .tabset-fade .tabset-pills}

## Predictor

RFモデルを例にやってみる

モデルとテストデータをInputして`Predictor`オブジェクトを作る

```{r}
X <- apartmentsTest %>% select(-m2.price)
Y <- apartmentsTest$m2.price
predictor.rf <- iml::Predictor$new(tuned.model[["rf"]], data = X, y = Y)
```

## Feature Importance

Permutation Errorも返してくれる

```{r}
imp <- iml::FeatureImp$new(predictor.rf, loss = "mae")
plot(imp)
print(imp)
```

## Partial dependence Plot - PDP

ある特徴量以外を固定したときの平均的な変化的なやつ

```{r}
pdp.obj <- iml::Partial$new(predictor.rf, feature = "construction.year")
plot(pdp.obj)
```

```{r}
pdp.obj$set.feature("surface")
pdp.obj$center(min(apartmentsTest$surface))
plot(pdp.obj)
```
